Modelling the Co-evolution of Trade and Culture in Past Societies

### 2015-07-02 article.tex
result p-value for N=250
small edits to the text

\paragraph{Production}
\todo{what is some, what is n}
Each agent produces one good. The type of good produced by an agent $i$ is assigned to it at the beginning of the simulation, does not change through the simulation and is referred as $produced^i$. At each time step, each agent, produces $n$ units of its production good, which ensures that enough is owned to be traded for other goods. Moreover, when an agent consumes its own production good, it does not impact its inventory.

@@

The neutral model is tested through 15 experimental setups. The first six experimental setups are using 1 good, two population sizes (250 and 500 agents) and three values of $\mu$ (0.004,0.016 and 0.064). The remaining experimental setups are using 500 agents, 3 number of goods (3,6 and 9) and three values of $\mu$ (0.004,0.016 and 0.064). For each setup we have performed 100 runs of 10000 timestep each.

The trading model is tested through four experimental setups using 3 goods, 500 agents and the same four values of $\mu$ (0.004,0.016 and 0.064). Again 100 runs of 10000 timesteps are performed.

The complete set of parameters tested on both models is presented in table~\ref{tab:parameters}.

@@

In order to understand the effect of introducing trading mechanisms, we compare first the distribution of values obtained in the ``trading model'' against the values obtained in the ``neutral model''. The figure~\ref{fig:2setDi}.a) presents the results obtained from 100 runs for each model. All runs rely on the same experimental setup using 3 goods, 500 agents and $\mu$ equal to 0.004. In all following graph  a variant is one price for one given good. All goods are thus studied independently.

>>>>

\paragraph{Production}

Each agent produces one good. The type of good produced by an agent $i$ is assigned to it at the beginning of the simulation, does not change through the simulation and is referred as $produced^i$. At each time step, each agent, produces a number of units (of its production good) equal to the number of goods, which ensures that enough is owned to be traded for other goods. Moreover, when an agent consumes its own production good, it does not impact its inventory.

@@

The neutral model is tested through 15 experimental setups. The first six experimental setups are using 1 good, two population sizes (250 and 500 agents) and three values of $\mu$ (0.004,0.016 and 0.064). The remaining experimental setups are using 500 agents, 3 number of goods (3,6 and 9) and three values of $\mu$ (0.004,0.016 and 0.064). For each setup we have performed 100 runs of 10000 timestep each. The trading model is tested on an experimental setups using 3 goods, 500 agents and $\mu$ equal to 0.004. Again 100 runs of 10000 timesteps are performed. The complete set of parameters tested on both models is presented in table~\ref{tab:parameters}.

@@

In order to understand the effect of introducing trading mechanisms, we compare first the distribution of values obtained in the ``trading model'' against the values obtained in the ``neutral model''. The figure~\ref{fig:2setDi}.a) presents the results obtained from 100 runs for each model. All runs rely on the same experimental setup using 3 goods, 500 agents and $\mu$ equal to 0.004. In all following graph  a variant is one price for one given good. The distributions are first computed for each good independently and then averaged together.
